\begin{thebibliography}{10}

\bibitem{bournez11:_solvin_analy_differ_equat_in}
O. Bournez, D. Gra{\c c}a, and A. Pouly.
\newblock Solving analytic differential equations in polynomial time over unbounded domains.
\newblock In {\em Proceedings of the 36th International Symposium on Mathematical Foundations of Computer Science} (MFCS), 
LNCS 6907, 170--181, 2011.

\bibitem{coddington1955theory}
E.A. Coddington and N.~Levinson.
\newblock {\em Theory of Ordinary Differential Equations}.
\newblock McGraw-Hill, 1955.

\bibitem{kawamura2010complexity}
A.~Kawamura.
\newblock Complexity of initial value problems.
\newblock To appear in {\em Fields Institute Communications}.

\bibitem{kawamura2010lipschitz}
A.~Kawamura.
\newblock Lipschitz continuous ordinary differential equations are
  polynomial-space complete.
\newblock {\em Computational Complexity}, 19(2):305--332, 2010.

\bibitem{kawamura11:_funct_space_repres_and_polyn_time_comput}
A.~Kawamura.
\newblock On function space representations and polynomial-time computability.
\newblock Dagstuhl Seminar 11411: Computing with Infinite Data, 2011.
% \newblock http://www-imai.is.s.u-tokyo.ac.jp/{\~{}}kawamura/dagstuhl.pdf.

\bibitem{kawamura2010operators}
A.~Kawamura and S.~Cook.
\newblock Complexity theory for operators in analysis.
\newblock \emph{ACM Transactions on Computation Theory}, 4(2), Article 5, 2012.

\bibitem{kawamura12:_unifor_polyt_comput_operat_univar}
A. Kawamura, N. M{\"u}ller, C. R{\"o}snick, and M. Ziegler.
\newblock Parameterized uniform complexity in numerics: from smooth to analytic, from NP-hard to polytime. 
\newblock http://arxiv.org/abs/1211.4974. 
% \newblock In {\em Proceedings of the Ninth International Conference on Computability and Complexity in Analysis}, 2012.

\bibitem{ko1983computational}
K.I. Ko.
\newblock On the computational complexity of ordinary differential equations.
\newblock {\em Information and Control}, 58(1-3):157--194, 1983.

\bibitem{ko1991complexity}
K.I. Ko.
\newblock {\em Complexity Theory of Real Functions}.
\newblock Birkh{\"a}user Boston, 1991.

\bibitem{ko1988computing}
K.I. Ko and H.~Friedman.
\newblock Computing power series in polynomial time.
\newblock {\em Advances in Applied Mathematics}, 9(1):40--50, 1988.

\bibitem{miller1970recursive}
W.~Miller.
\newblock Recursive function theory and numerical analysis.
\newblock {\em Journal of Computer and System Sciences}, 4(5):465--472, 1970.

\bibitem{muller1987uniform}
N.T. M{\"u}ller.
\newblock Uniform computational complexity of {T}aylor series.
\newblock {\em Automata, Languages and Programming}, pages 435--444, 1987.

\bibitem{pour1979computable}
M.B. Pour-El and I.~Richards.
\newblock A computable ordinary differential equation which possesses no
  computable solution.
\newblock {\em Annals of Mathematical Logic}, 17(1-2):61--90, 1979.

\bibitem{toran1991complexity}
J.~Tor{\'a}n.
\newblock Complexity classes defined by counting quantifiers.
\newblock {\em Journal of the ACM}, 38(3):752--773, 1991.

\bibitem{wagner1986complexity}
K.W. Wagner.
\newblock The complexity of combinatorial problems with succinct input
  representation.
\newblock {\em Acta Informatica}, 23(3):325--356, 1986.

\bibitem{weihrauch00:_comput_analy}
K. Weihrauch.
\newblock {\em Computable Analysis: An Introduction}.
\newblock Texts in Theoretical Computer Science. Springer, 2000.
\end{thebibliography}
